Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-20 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}

@@

\noindent where the variable $autonomy$ is a design definition; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
Secondly, the total (minimum) number of batteries is computed as 
\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \frac{V_{system}}{V_{bat}} \times \frac{C_{bank}}{Battery \, Capacity}.
\end{equation}

Regarding the charge controller, it must initially meet the voltage requirement of the PV system, as described by Eq.~\ref{eq:vcvsystem} to the charge controller voltage:

@@

The short circuit reference from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature is higher than the nominal or laboratory temperature, and PV system is temperature dependent:

\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = \frac{G}{G_{ref}} \left[I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
\end{equation}

The controller must meet the maximum current from the PV array given as
%
\begin{equation}
\label{eq:icmin}
I_{c,min} = I_{sc,amb} \times N_{PP},
\end{equation}

@@

The inverter sizing check is performed by means of three equations. Eq.~\ref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\ref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\ref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.

@@

\textcolor{red}{did we address this comment of the ASE reviewer? ``In some of the equations, the variables are not typed. In CPS some of the variables may belong to continuous domains (real numbers). You need to explain the types for variables and justify that the underlying verification tool supports those types.'' I think we should make it explicit in this section.}

@@

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------

%---------------------------------------------------------------------------
\subsection{Description of the Case studies}
%---------------------------------------------------------------------------

We have performed seven case studies to evaluate our proposed synthesis approach, as described in the first column of Table~\ref{tab1} 
(\textit{Specification}) \textcolor{red}{shall we make this table available online?}. These case studies were defined based on the usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{Agrener2013,TrindadeCordeiro19}. Except for case 7 that was idealized as a small-town solution to support only a few lamps and a 12k BTUs air-conditioner. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems. Furthermore, three start-of-art verifiers, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used to compare our approach effectiveness and efficiency.

@@

Concerning the off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis. Here we used HOMER Pro as a state-of-the-art simulation tool for comparison purposes. In particular, HOMER Pro has the following characteristics:

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB of RAM running Windows 10. \textcolor{red}{we have to explain here why we have used two different hardware platform. Does it influence on the results?}. We We perform the experiments with a predefined time out of $240$ minutes.

@@

CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes. The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG2} and \textit{EG3} \textcolor{red}{why? explain it here...}.

@@

Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro. In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. In this respect, even the manufacturer's brand can be presented (\textcolor{red}{shall we add this table online?} in Table~\ref{tab1} it was removed to avoid some advertising).

\begin{table}[!t]
\caption{Case studies and results: optimization of PV systems \textcolor{red}{could you please put this table online?}.}\label{tab1}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell {ESBMC 6.0.0\\(Boolector 3.0.1)} & HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & OM & TO & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & OM & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & OM & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} &  \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & OM & TO & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & OM & TO & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & OM & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & TO & OM & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Caption: OM= out of memory; TO= timeout; E= energy, NTP= total number of panels, NBT= total number of batteries, LCC= life cicle cost.
\end{table}

%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%

>>>>

\begin{wrapfigure}{r}{0.5\textwidth}
%\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{wrapfigure}

@@

\noindent where the variable $autonomy$ is a design definition; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery depth of discharge (considered of maximum of 25\% here).
Secondly, the total (minimum) number of batteries $N_{B}total$ is computed as a product of the minimum number of batteries in series $N_{BS}min$ with the minimum number of batteries in parallel $ N_{BP}min $ and, therefore, as function of battery bank capacity $ C_{bank} $ and the capacity of the chosen battery $ Battery \, Capacity $ as

\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \frac{V_{system}}{V_{bat}} \times \frac{C_{bank}}{Battery \, Capacity}.
\end{equation}

Regarding the charge controller, it must initially meet the voltage requirement of the PV system $V_{system}$, as described by Eq.~\ref{eq:vcvsystem} to the charge controller voltage $V_{c}$:

@@

The short circuit reference current $ I_{sc,ref} $ from the manufacturer's solar panel must be corrected to the cell temperature because the field temperature $ T $ is higher than the nominal or laboratory temperature, and PV system is temperature dependent. This corrected current is called $I_{sc,amb}$, it uses $G_{ref} = 1000$ and the ratio of current change over temperature $\mu_{I}$:

\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = \frac{Solar \, Irradiance}{G_{ref}} \left[I_{sc,ref} + \mu_{I} \times (T-25) \right]. 
\end{equation}

The controller must meet the maximum current from the PV array. Therefore the controller current $I_{c}$ must be less than the calculated $I_{c,min}$ and given as
%
\begin{equation}
\label{eq:icmin}
I_{c,min} = I_{sc,amb} \times N_{PP},
\end{equation}

@@

The inverter sizing check is performed by means of three equations. Eq.~\ref{eq:vindc} ensures that the input voltage of the controller $V_{in}DC$ meets the system voltage. Eq.~\ref{eq:voutac} ensures that the output voltage of the controller $V_{out}AC$ meets the AC voltage of the load $V_{AC}$. Finally, Eq.~\ref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $P_{AC,ref}$ is the nominal power and $MAX_{AC,ref}$ is the peak power that the inverter can support.

@@

\textcolor{red}{In CPS some of the variables may belong to continuous domains (real numbers).  All the equations illustrated here produces real numbers, although when choosing batteries and panels quantities those real numbers must be translated into integer number (closest ones, considering the minimum or maximum according with each equation). The underlying verification tool and the simulation tool must support those type of variables in order to produce a correct result.}

@@

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
%---------------------------------------------------------------------------
\subsection{Description of the Case studies}
%---------------------------------------------------------------------------
The proposed synthesis approach was evaluated in  seven stand-alone PV system case studies: 
\textbf{case study 1:} power peak: 342 W, power surge: 342 W, energy consumption: 3,900 Wh/day, battery autonomy: 48 h; \textbf{case study 2:} Power peak: 814 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 48 h; \textbf{case study 3:} power peak: 815 W, power surge: 980 W, energy consumption: 4,880 Wh/day, battery autonomy: 12 h; \textbf{case study 4:} power peak: 253 W, power surge: 722 W, energy consumption: 3,600 Wh/day, battery autonomy: 48 h; \textbf{case study 5:} power peak: 263 W, power surge: 732 W, energy consumption: 2,500 Wh/day, battery autonomy: 48 h; \textbf{case study 6:} power peak: 322 W, power surge: 896 W, energy consumption: 4,300 Wh/day, battery autonomy: 48 h; \textbf{case study 7:} power peak: 1,586 W, power surge: 2,900 W, energy consumtion: 14,000 Wh/day, battery autonomy: 48 h.

These case studies were defined based on the usual electrical load found in riverside communities in the State of Amazonas,  Brazil~\cite{TrindadeCordeiro19,Agrener2013}, with the exception of case 7, that was idealized as a small town solution to support a few lamps and a 12 kBTUs air-conditioner. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems.

Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.

@@

Concerning the off-the-shelf simulation tools, only HOMER Pro performs off-grid system with battery backup analysis and includes economical analysis. Here we used HOMER Pro version $3.13.1$ as a state-of-the-art simulation tool for comparison purposes. In particular, HOMER Pro has the following characteristics:

@@

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB of RAM running Windows 10. \textcolor{red}{The hardware platform was not the same because of the availability of the machines, and this has impact in respect to the performance that is less favorable to HOMER Pro}. We perform the experiments with a predefined time out of $240$ minutes.

@@

A Table with the details of the results is present on-line\footnote{\url{https://drive.google.com/file/d/1I1Cg4FNz9grMqXHUmOKnd-\_PFmLpmk6m/view?usp=sharing}}. Summarizing,  CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes. The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG2} and \textit{EG3} \textcolor{red}{why? explain it here...}.

@@

Our synthesis tool can present a solution, which is far detailed and closer to the commercial reality than the solution presented by HOMER Pro. In particular, our automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from datasheet of manufacturers, including the model of the component, nominal current, and voltage. In this respect, even the manufacturer's brand can be presented (\textcolor{red}{shall we add this table online?} in Table~\ref{tab1} it was removed to avoid some advertising).
%
% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{trindadeThesis}
%
